Quantifying the home ground advantage with `hyper2` and `hyper3` objects

### 2025-02-14 inst/home_advantage.Rmd
work

```{r,label=loopysuppcalc,cache=TRUE}
probs <- seq(from=0.1,to=0.8,len=17)
jj <- as.matrix(expand.grid(lam,probs))
S <- rep(NA,nrow(jj))
for(i in seq_len(nrow(jj))){
    lambda <- jj[i,1]
    p1 <- jj[i,2]
    p <- c(p1,1-p1)
    names(p) <- c("p1","p2")
   S[i] <- loglik(p=p,H=home_away3(M,lambda=lambda),log=TRUE)
}
S <- matrix(S,length(lam),length(probs))
```

@@

```{r, bbdlambdaD,cache=TRUE}
aT
home_draw_away3(aT,lambda=1.888,D=0.3)
f <- function(v){
    H <- home_draw_away3(aT, lambda = v[1], D=v[2])
    maxp(H,give=1)$`Log-likelihood`
}
n <- 20
lambda_try <- seq(from=1.6,to=4,len=n)
D_try <- seq(from=0.3,to=1,len=n)
V <- as.matrix(expand.grid(lambda_try,D_try))
LL <- apply(V,1,f)
```

@@

>>>>

```{r,label=loopysuppcalc,cache=TRUE}
probs <- seq(from=0.1,to=0.8,len=2)
jj <- as.matrix(expand.grid(lam,probs))
S <- rep(NA,nrow(jj))
for(i in seq_len(nrow(jj))){
    lambda <- jj[i,1]
    p1 <- jj[i,2]
    p <- c(p1,1-p1)
    names(p) <- c("p1","p2")
   S[i] <- loglik(p=p,H=home_away3(M,lambda=lambda),log=TRUE)
}
S <- matrix(S,length(lam),length(probs))
```

@@

```{r, bbdlambdaD,cache=TRUE}
aT
home_draw_away3(aT,lambda=1.888,D=0.3)
f <- function(v){
    H <- home_draw_away3(aT, lambda = v[1], D=v[2])
    maxp(H,give=1)$`Log-likelihood`
}
n <- 20
lambda_try <- seq(from=1,to=3,len=n)
D_try <- seq(from=0.1,to=0.6,len=n)
V <- as.matrix(expand.grid(lambda_try,D_try))
LL <- apply(V,1,f)
```

@@

Now find the evaluate:

```{r findtheevaluate, cache=TRUE}
maxv <- optim(par=c(3,0.7), fn=f, control=list(fnscale = -1))
```

```{r showtheevaluate}
maxv
```

```{r usetheevaluatefindmax, cache=TRUE}
MLparams <- maxv$par
mH <- maxp(home_draw_away3(aT, lambda = MLparams[1], D=MLparams[2]),give=1)
```

```{r}
mH
```
